Assessment of simulation procedures and robust methods for Mendelian randomization analysis

### 2022-11-12 presentation/robustMR.qmd
updated figures, figure01 quadrant function

t(filter_FTO) %>% kable() %>% 
  kable_styling(font_size=18)
```

@@

-   Simulation study: 
    -   Start with sample size of 50,000 and ~9 IVs (depending on how many remain after harmonizing datasets)
    -   Simulate for all significant IVs $\beta_{X_{sim}}$ from a normal distribution $\beta_{X_{sim}} \sim N(\beta_{\hat X_{IV}}, \hat se_{X_N})$ and $\beta_{X_{sim}}$ from a normal distribution $\beta_{Y_{sim}} \sim N(\beta_{\hat Y_{IV}}, \hat se_{Y_N})$; start with $n_{sim}=100$
    -   Simulate $maf$ from a Binomial distribution with $maf_{X_{sim}} \sim Bin(maf, 2N)$ 
        - This I did not fully understand: We do not want to count the successes, but simulate the $maf$. Should we draw it from a normal distribution too?

>>>>

t(filter_FTO) %>% kable() %>% 
  kable_styling(font_size=14)
```

@@

-   Simulation study: 
    -   Start with sample size of 50,000 and ~9 IVs (depending on how many remain after harmonizing datasets)
    -   Simulate for all significant IVs $\beta_{X_{sim}}$ from a normal distribution $\beta_{X_{sim}} \sim N(\beta_{\hat X_{IV}}, \hat se_{X_N})$ and $\beta_{Y_{sim}}$ from a normal distribution $\beta_{Y_{sim}} \sim N(\beta_{\hat Y_{IV}}, \hat se_{Y_N})$; start with $n_{sim}=100$
    -   Simulate $maf$ from a Binomial distribution with $maf_{X_{sim}} \sim Bin(maf, 2N)$ 
        - This I did not fully understand: Should we draw the proportion $maf$ from a normal distribution (with $\mu=\hat {maf}$ and $sd=?$) too?
    -   Choose simulated beta estimates (exposure/ outcome) and compare causal estimates of different MR methods with causal estimate from original study (n~300,000) and with biologic plausible estimate (Wald estimate from FTO gene as single IV)
        - Calculate Bias, Variance and MSE

-   From figure 2: SNPs were divided into 4 grouls -> Repeat simulation for SNPs from each group
